Functional Enrichment Tests: Intro and methods comparison

### 2023-06-15 DRAFT_Funct_Enrich.Rmd
Add html knit of draft w/ stats intro

##Fisher’s Exact Test

@@

$a =$ $n$ genes of GO term $i$ in both the test and background set
$b =$ $n$ genes of GO $i$ in the background but not test
$c =$ $n$ genes of GO $i$ absent from the test but present in the background
$d =$ $n$ genes of GO $i$ absent in both the category and the background
$n =$ $n$ genes in the background set

@@

##Mann Whitney U Test

@@

$a =$ $n$ genes in GO term $i$
$b =$ $n$ genes in the background set

>>>>

## Fisher’s Exact Test

@@

* $a =$ $n$ genes of GO term $i$ in both the test and background set
* $b =$ $n$ genes of GO $i$ in the background but not test
* $c =$ $n$ genes of GO $i$ absent from the test but present in the background
* $d =$ $n$ genes of GO $i$ absent in both the category and the background
* $n =$ $n$ genes in the background set

@@

## Mann Whitney U Test

@@

* $a =$ $n$ genes in GO term $i$
* $b =$ $n$ genes in the background set
